Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2024-03-12 incidence-prevalence.tex
restructure sec 7.1

Considering multiple values of $t$ makes \cref{inc-prev:eq:EPt} into a system of simultaneous equations.
The system can be written in the form $\E(\vec{P} \mid \vec{Z}) = \matr{S} \vec{Z}$ where $\matr{S}$ is a lower-triangular matrix formed from $S$:
\begin{align}
    (\matr{S})_{i,j} = \begin{cases}
        S(i - j + 1) & i - \dmax - 1 \leq j \leq i \\
        0 & \text{otherwise.}
    \end{cases}
\end{align}
In \cref{E-backcalc}, I will need to solve for this system for $\vec{Z}$ given a known $\hat{P} = \E(\vec{P} \mid {Z})$.
As $\matr{S}$ is lower-triangular, I use forward-substitution~\autocite{cormenMatrix}.
Forward-substitution sequentially solves the $t$th element of $\vec{Z}$ ($t = 1, \dots, T$) by calculating:
\begin{align}
Z_t
&= \frac{\hat{P}_t - \sum_{i=1}^{t-1} S_{ti} Z_i}{S_{tt}} \\
&= \hat{P}_t - \sum_{i=1}^{t-1} S(t - i + 1) Z_i.
\label{inc-prev:eq:forward-substitute}
\end{align}

>>>>

Considering multiple values of $t$ makes \cref{inc-prev:eq:EPt} into a system of simultaneous equations.
Therefore, the system can be written in matrix form:
\begin{align}
  \E(\vec{P} \mid \vec{Z}) = \matr{S} \vec{Z}. \label{inc-prev:eq:EPt-matrix} \\
\intertext{$\matr{S}$ is a lower-triangular matrix formed from $S$:}
    (\matr{S})_{i,j} &= \begin{cases}
        S(i - j + 1) & i - \dmax - 1 \leq j \leq i \\
        0 & \text{otherwise.}
    \end{cases} \label{inc-prev:eq:Smatrix}
\end{align}
In \cref{E-backcalc}, I will need to solve for this system for $\vec{Z}$ given a known $\hat{P} = \E(\vec{P} \mid {Z})$.
As $\matr{S}$ is lower-triangular, I use forward-substitution~\autocite{cormenMatrix}.
Forward-substitution sequentially solves the $t$th element of $\vec{Z}$ ($t = 1, \dots, T$) by calculating:
\begin{align}
Z_t
&= \frac{\hat{P}_t - \sum_{i=1}^{t-1} S_{ti} Z_i}{S_{tt}} \\
&= \hat{P}_t - \sum_{i=1}^{t-1} S(t - i + 1) Z_i.
\label{inc-prev:eq:forward-substitute}
\end{align}

### 2024-03-12 transmission.tex
restructure sec 7.1

In this section, I will apply the theory introduced in \cref{E-inc-prev} to estimate incidence.
% First, I explain the method I will apply (\cref{backcalc:sec:methods}) and then present the results (\cref{backcalc:sec:results}).
% I discuss the results in \cref{backcalc:sec:discussion} and conclude in \cref{backcalc:sec:conclustion}.

In \cref{E-inc-prev:sec:observation-process}, I showed that a deterministic approximation to the relationship between true prevalence and incidence is a good approximation for estimating incidence.
This relationship between incidence proportion and prevalence means that once one is inferred, the other is calculated via a deterministic function.
Therefore, a statistical methodology for estimating one of these quantities is required.

Estimation of prevalence from the CIS data was carried out using MRP throughout the pandemic (see \cref{E-biology-data:sec:MRP}).
In this section, I propose extending this process by transforming the posterior distribution of prevalence in each stratum to a posterior distribution of incidence before the poststratification step.

% I keep the same logistic regression model for predicting prevalence, then transform its posterior distribution of prevalence to a posterior distribution of incidence.
This results in a two-step process: first, the same inference process described in \cref{E-biology-data:sec:MRP} is used to estimate prevalence; second, the prevalence is transformed to incidence.
This is required to fulfil several desirable features of the model.

An alternative would be an inference procedure that estimates incidence proportion, fit directly to the RT-PCR test results.
Denote the quantity to be inferred (which could be either incidence proportion or prevalence) at time $t$ in strata $i$ as $\pi_{it}$.
The strata are defined by at least age group, region, ethnicity, and sex due to differential non-response in the survey (see \cref{E-intro:sec:cis-strata}).
For many combinations of stratum $i$ and day $t$, the number of positives will be small, often fewer than 5; therefore some form of borrowing between time and strata is required.
The statistical model and inference procedure should have the following properties.
\begin{enumerate}
    \item The smoothing model over time should penalise changes from continuous exponential growth.
        Penalising changes from continuous exponential growth is a natural formulation because mechanistic models predict exponential growth over short periods of time.
        Furthermore, such penalisation has previously been shown to improve estimates of SARS-CoV-2 prevalence by balancing over and under-fitting~\autocite{ealesAppropriately}.
    \item Limit estimates to epidemiologically and biologically plausible values.
        That is, incidence proportion and prevalence should be in the interval $[0, 1]$.
        % While incidence proportion can theoretically be greater than 1, this would imply that some individuals were infected multiple times in a day which is not biologically plausible.
    \item Have sufficient parameters to incorporate all necessary covariates to correct for non-response bias (see \cref{E-biology-data:sec:cis}).
    \item Borrow information across the different covariates.
        The borrowing should penalise changes in the distribution of incidence/prevalence across strata in the same geographic region being constant.
        Standard stratified, mechanistic transmission model (such as the one introduced in \cref{E-SEIR:sec:structured-populations}) predict this, if behavioural changes are independent of strata and there is negligible impact of immunity.
    \item Be computationally efficient.
        The model will be fit to granular data and therefore needs to be run within the SRS, with its computational limitations (see \cref{E-biology-data:sec:SRS}).
\end{enumerate}

Properties 1 and 2 suggest a model of the form $\logit(\pi_{it}) = g(i, t)$, where $g$ is a function with changes in the first derivative penalised (\ie changes away from linear are penalised).
The $\logit$ link function both limits $\pi_{it}$ to the interval $[0, 1]$, and logit-linear growth approximates exponential growth for small $\pi_{it}$~\autocite{ealesAppropriately}.
Combined with property 4, the form of $g$ the null model is $g(i, t) = a_0 + a_t t + f(i)$ where $a_0$ and $a_t$ are model parameters and $f$ is a function to be specified; that is, changes away from this model should be penalised.

@@

\todo[inline]{Is it OK that $x$ and $y$ in the following two paragraphs don't align with the rest of the thesis chapter? Should I use alterantive notation - but then different to standard in the INLA papers.}
INLA-based inference can only be applied to LGMs (\emph{Latent Gaussian Models})~\autocite{rueINLAseminar,rueINLA,martinoINLAtutorial}; see \cref{E-transmission:sec:INLA} for further details on INLA.
An LGM is defined in terms of a vector of hyperparameters, $\vec{\varphi}$; a deterministic transformation of the hyperparameters into covariance matrix, $\matr{\Sigma}(\vec{\varphi})$; a vector of latent variables, $\vec{x}$; a vector of $n$ data points, $\vec{y} = [y_1, \dots, y_n]^T$; and $n$ linear predictors $\vec{\eta} = [\eta_1, \dots, \eta_n]^T$.
To be an LGM, $\vec{x}$ must be a latent Gaussian field, that is $\vec{x} \mid \vec{\varphi} \dist \N(\vec{0}, \matr{\Sigma}(\vec{\varphi}))$; and the likelihood must have the conditional independence property $p(\vec{y} \mid \vec{\varphi}, \vec{x}) = \prod_j p(y_j \mid \eta_j(\vec{x}), \vec{\varphi})$.

In this context, each $y_j$ corresponds to the observed RT-PCR results in one stratum on one day.
Hence, $\eta_{j}$ must determine the distribution of $y_{j}$ (up to some hyperparameters); where $j$ uniquely identifies a stratum $i$ and day $t$.
In practice, this means that $\eta_j$ is a one-to-one transformation of the population prevalence in stratum $i$ on day $t$.
If $\eta_j = \logit(\pi_{it})$, where $\pi$ is prevalence, then a model of $\eta_j = g(i, t)$, as before, is a LGM.
However, if $\pi$ is instead representing incidence proportion, then no such linear relationship between $\eta_j$ and $g$ exists.
In particular, if $\eta_j$ is the prevalence, then $\eta_{it} = \sum_{k=-\infty}^0 \pi_{ik} S(k) = \sum_{k=-\infty}^0 \expit(g(i, k)) S(k)$.
As $g(i, k)$ is linear in the model parameters, $\vec{x}$, then $\eta_{it}$ is not, violating the requirements of a LGM.
Therefore, the application of the INLA approximation, while satisfying the other desirable properties, requires that the regression model predicts RT-PCR prevalence, not incidence proportion.

Next, I explain how I extended the MRP model introduced in \cref{E-biology-data:sec:MRP} to calculate incidence.
I draw a sample of 500 prevalence time series in each stratum from the approximate posterior distribution (using the procedure described in \cref{transmission:sec:INLA:posterior}).
For each stratum, I use the relationship in \cref{E-inc-prev:eq:EPt} to calculate the incidence proportion at each time point.
I consider the relationship between incidence and prevalence within a stratum to be deterministic, as \cref{E-inc-prev:sec:observation-process} justifies, that is the estimate of the incidence is negligibly affected by approximating the distribution $\vec{P} \mid \vec{Z}$ by its mean.
I solve this system using forward substitution, calculating the value of $Z_t$ in \cref{E-inc-prev:eq:forward-substitute} sequentially for $t = 1, \dots, T$.
\Cref{E-inc-prev:eq:forward-substitute} is repeated here for convenience:
\begin{align}
Z_t
&= \frac{P_t - \sum_{i=1}^{t-1} S_{ti} Z_i}{S_{tt}} \\
&= P_t - \sum_{i=1}^{t-1} S(t - i + 1) Z_i.
\label{transmission:eq:forward-substitute}
\end{align}
% \Cref{E-inc-prev:eq:EPt}, considered across different values of $t$, can be written as $\vec{P} = \matr{S} \vec{Z}$, where: $\vec{P}$ is a vector of the number of prevalent individuals at each time point in the stratum; $\matr{S}$ is a matrix formed from the survival function, as defined below; and $\vec{Z}$ is a vector of the incidence at each time point in the stratum.
Dividing each side by the total number of individuals in each stratum transforms number of prevalent individuals to prevalence and incidence to incidence proportion.

Violation of assumptions in various parts of this procedure can lead to the second term in \cref{transmission:eq:forward-substitute} to be greater than the first, giving negative incidence.
In this case, the incidence prior to day $t$ imply that the prevalence on day $t$ is higher than that predicted by the fitted regression model for this strata/day combination.
There are two sets of assumptions which are most likely to be violated.
The first set of assumptions is in constructing survival matrix, $\matr{S}$, which is assumed to be known with no uncertainty in this procedure.
However, \cref{E-imperf-test} showed that the estimate of $S(t)$ is sensitive to assumptions made, such as the assumed $\psens$ and strength of priors used.
The second set of assumptions are in specifying the statistical model used to estimate prevalence, for example the form of the smoothing used.

@@

Alternative inference techniques could allow more powerful modelling approaches, if they allowed a broader set of models than LGMs.
In particular, the incidence proportion could be directly modelled rather than the prevalence.
This could allow more interpretable priors to be used because the infection process is the process that corresponds to biological and behavioural processes.
Furthermore, the incidence proportion could be restricted to be non-negative, preventing the negative incidence seen in some strata.

Various alternative inference techniques could be considered.
If the infection process is considered a Poisson process (see \cref{E-inc-prev:sec:poisson-process}), then, conditional on the process's intensity, there is independence between individuals' infection status.
Therefore, the incidence proportion and prevalence can both be viewed as the mean of many Bernoulli variables, meaning that the Central Limit Theorem suggests they are approximately normally distributed.
Exploiting this property could enable efficient approximations to the posterior.

@@

The majority of the confidence intervals contain the nominal probability (see \cref{SEIR:fig:sim-coverage}).
There is a tendency for the coverage to be slightly lower than the nominal probability, suggesting that the credible intervals are slightly too narrow.
This is a common issue with random walk MCMC (see \cref{E-inc-prev:sec:MCMC}).
The same issue arises with the coverage for derived quantities incidence and prevalence (see \cref{SEIR:fig:sim-inc-prev}).
\begin{figure}
    \includegraphics{SEIR/sim/coverage}
    \caption[Coverage of simulation study]{%
        Point estimate and 95\% confidence interval for coverage of the 50\%, 75\%, and 95\% central credible intervals for each parameter; see text for full definition.
        Vertical lines show the nominal coverage.
    }
    \label{SEIR:fig:sim-coverage}
\end{figure}
\begin{figure}
    \thisfloatpagestyle{empty}
    \vspace{-3cm}
    \makebox[\textwidth][c]{\includegraphics[width=0.9\paperwidth]{SEIR/sim/predictive_coverage}}
    \caption[Coverage of simulation study (derived quantities)]{%
        Point estimate and 95\% confidence interval for coverage of the 50\%, 75\%, and 95\% central credible intervals for (A) incidence and (B) prevalence; see main text for full definition.
        Horizontal lines show the nominal coverage.
    }
    \label{SEIR:fig:sim-inc-prev}
\end{figure}

@@

All regions' MCMC chains converged, assessed using the Rhat statistic and ESS (as defined in \cref{E-intro:sec:MCMC}).
The highest Rhat was 1.01 for $\sigma_\epsilon$ in London.
All parameters had ESS > 1000, except $\sigma_\epsilon$ and $\psi$ in London, which had ESS of 450 and 950 respectively.

>>>>

In this section, I will apply the theory introduced in \cref{E-inc-prev} to estimate incidence.
I view the CIS as a series of daily, cross-sectional prevalence surveys.
This is the same approach as previously used to estimate prevalence from the CIS (see \cref{E-biology-data:sec:MRP}).

An important consideration in this section is the non-response bias.
I adopt the poststratification method introduced in \cref{E-biology-data:sec:MRP} to correct for this bias.
Therefore, incidence must be estimated in each stratum before being poststratified to the target population and subpopulations of interest.
The strata are defined by at least age group, region, ethnicity, and sex due to differential non-response in the survey (see \cref{E-intro:sec:cis}).

\subsection{Approach} \label{backcalc:sec:approach}

In \cref{E-inc-prev:sec:observation-process}, I showed that a deterministic approximation to the relationship between true prevalence and incidence is a good approximation for estimating incidence.
This relationship between incidence proportion and prevalence means that once one is inferred, the other is calculated via a deterministic function.
This gives two possible approaches for estimating incidence from prevalence data.

\subsubsection{Possible approaches}

The first approach, which I call the \emph{incidence-inferred} approach, is a single statistical model where incidence is inferred, with prevalence as a derived quantity.
The basis of the statistical model, in a Bayesian framework, would be as follows.
\begin{align}
    \vec{Z} \mid \vec{\phi} &\dist g_Z(\vec{\phi}) \\
    P_{i,t} &= \matr{S} \vec{Z}_i \\
    Y_{i,t} \mid \vec{P} &\dist \BB(n_{i,t}, P_{i,t})
\end{align}
where $\vec{Z}$ is a vector of incidence proportion for each strata and day defined by some model $g$ with parameters $\vec{\phi}$; $P_{i,t}$ is the prevalence in stratum $i$ on day $t$; $\matr{S}$ is the survival matrix defined in \cref{E-inc-prev:eq:Smatrix}; $Y_{i,t}$ is the number of positive tests in stratum $i$ on day $t$; and $n_{i,t}$ is the number of tests in stratum $i$ on day $t$.
The model $g_Z$ would be specified to share information across time and/or strata.
This both helps stabilise the estimation (see\todo{ref wherever I end up explaining backcalculation stability issues}) and allows borrowing of information across strata.
Borrowing information is required because some strata and time combinations have few positives (fewer than five per day).
The relationship between $P$ and $Z$ is from \cref{E-inc-prev:eq:EPt-matrix}, although dividing both sides by $\Npop$ to have the values in terms of incidence proportion and prevalence rather than incidence and number of prevalent individuals.

The second approach, which I call the \emph{prevalence-inferred} approach takes a two-step approach.
First, it uses the statistical model from \cref{E-biology-data:sec:MRP} to estimate prevalence.
Then, it transforms the posterior distribution of prevalence to a posterior distribution of incidence using the forward substitution as in \cref{E-inc-prev:eq:forward-substitute}.
At a high-level, the statistical model is:
\begin{align}
    \vec{P} \sim \vec{\phi} &\dist g_P(\vec{\phi}) \\
    Y_{i,t} &\dist \BB(n_{i,t}, P_{i,t})
\end{align}
where $g_P$ is analogous to $g_Z$ in providing a joint prior for the prevalence in each strata and day combination.

\subsubsection{Desirable properties}

The incidence-inferred approach is more parsimonious in being a single step procedure.
However, it poses several pragmatic challenges which means I favour the prevalence-inferred approach.
Here I explain that further developments, beyond the scope of this thesis, would be required to use the incidence-inferred approach with a suitable $\pi_Z$ within the computational constraints of the SRS.

Denote the quantity to be inferred at time $t$ in strata $i$ as $\pi_{i,t}$.
That is, under the incidence-inferred approach, $\pi_{i,t}$ is the incidence proportion, and under the prevalence-inferred approach, $\pi_{i,t}$ is the prevalence.

The chosen approach should have the following properties.
\begin{enumerate}
    \item The smoothing model over time should penalise changes from continuous exponential growth.
        Penalising changes from continuous exponential growth is a natural formulation because mechanistic models predict exponential growth over short periods of time.
        Furthermore, such penalisation has previously been shown to improve estimates of SARS-CoV-2 prevalence by balancing over and under-fitting~\autocite{ealesAppropriately}.
    \item Limit estimates to epidemiologically and biologically plausible values.
        That is, incidence proportion and prevalence should be in the interval $[0, 1]$.
        % While incidence proportion can theoretically be greater than 1, this would imply that some individuals were infected multiple times in a day which is not biologically plausible.
    \item Have sufficient parameters to incorporate all necessary covariates to correct for non-response bias.
    \item Borrow information across the different covariates.
        The borrowing should penalise changes in the distribution of incidence/prevalence across strata in the same geographic region being constant.
        A constant distribution is predicted by the theoretical study of epidemics, for example the dynamics of stratified, mechanistic transmission models (such as the one introduced in \cref{E-SEIR:sec:structured-populations}) over short periods of time with negligible behavioural and immunity changes.
    \item Be computationally efficient
        The model will be fit to granular data and therefore needs to be run within the SRS, with its computational limitations (see \cref{E-biology-data:sec:SRS}).
\end{enumerate}

Properties 1 and 2 suggest a model of the form $\logit(\pi_{i,t}) = g(i, t)$, where $g$ is a function with changes in the first derivative penalised (\ie changes away from linear are penalised).
The $\logit$ link function both limits $\pi_{i,t}$ to the interval $[0, 1]$, and logit-linear growth approximates exponential growth for small $\pi_{i,t}$~\autocite{ealesAppropriately}.
Combined with property 4, the form of $g$ the null model is $g(i, t) = a_0 + a_t t + f(i)$ where $a_0$ and $a_t$ are model parameters and $f$ is a function to be specified; that is, changes away from this model should be penalised.

@@

INLA-based inference can only be applied to LGMs (\emph{Latent Gaussian Models})~\autocite{rueINLAseminar,rueINLA,martinoINLAtutorial}; see \cref{E-transmission:sec:INLA} for further details on INLA.

An LGM is defined in terms of a vector of hyperparameters, $\vec{\varphi}$; a deterministic transformation of the hyperparameters into covariance matrix, $\matr{\Sigma}(\vec{\varphi})$; a vector of latent variables, $\vec{z}$; a vector of $n$ data points, $\vec{w} = [w_1, \dots, w_n]^T$; and $n$ linear predictors $\vec{\eta} = [\eta_1, \dots, \eta_n]^T$.
To be an LGM, $\vec{z}$ must be a latent Gaussian field, that is $\vec{z} \mid \vec{\varphi} \dist \N(\vec{0}, \matr{\Sigma}(\vec{\varphi}))$; and the likelihood must have the conditional independence property $p(\vec{w} \mid \vec{\varphi}, \vec{z}) = \prod_j p(w_j \mid \eta_j(\vec{z}), \vec{\varphi})$.

In this context, each $w_j$ corresponds to the observed RT-PCR results in one stratum on one day.
Hence, $\eta_{j}$ must determine the distribution of $w_{j}$ (up to some hyperparameters); where $j$ uniquely identifies a stratum $i$ and day $t$.

In practice, this means that $\eta_j$ is a one-to-one transformation of the population prevalence in stratum $i$ on day $t$.
If $\eta_j = \logit(\pi_{i,t})$, where $\pi$ is prevalence, then a model of $\eta_j = g(i, t)$, as before, is a LGM.
However, if $\pi$ is instead representing incidence proportion, then no such linear relationship between $\eta_j$ and $g$ exists.
In particular, if $\eta_j$ is the prevalence, then:
\begin{align}
    \eta_{i,t}
    &= \sum_{k=-\infty}^0 \pi_{ik} S(k) \\
    &= \sum_{k=-\infty}^0 \expit(g(i, k)) S(k).
\end{align}
As $g(i, k)$ is linear in the model parameters, $\vec{z}$, then $\eta_{i,t}$ is not, violating the requirements of a LGM.

Therefore, using the INLA approximation while satisfying the other desirable properties requires that $g$ predicts prevalence, not incidence proportion.
Hence, I adopt the prevalence-inferred approach.

Now I explain how I extended the MRP model introduced in \cref{E-biology-data:sec:MRP} to implement the prevalence-inferred approach.

First, I draw a sample of 500 prevalence time series in each stratum from the approximate posterior distribution (using the procedure described in \cref{transmission:sec:INLA:posterior}).
For each stratum, I use the relationship in \cref{E-inc-prev:eq:EPt} to calculate the incidence proportion at each time point.
I consider the relationship between incidence and prevalence within a stratum to be deterministic, as \cref{E-inc-prev:sec:observation-process} justifies, that is the estimate of the incidence is negligibly affected by approximating the distribution $\vec{P} \mid \vec{Z}$ by its mean.
I solve this system using forward substitution, calculating the value of $Z_t$ in \cref{E-inc-prev:eq:forward-substitute} sequentially for $t = 1, \dots, T$.
\Cref{E-inc-prev:eq:forward-substitute} is repeated here for convenience:
\begin{align}
Z_t
&= \frac{P_t - \sum_{i=1}^{t-1} S_{ti} Z_i}{S_{tt}} \\
&= P_t - \sum_{i=1}^{t-1} S(t - i + 1) Z_i.
\label{transmission:eq:forward-substitute}
\end{align}
% \Cref{E-inc-prev:eq:EPt}, considered across different values of $t$, can be written as $\vec{P} = \matr{S} \vec{Z}$, where: $\vec{P}$ is a vector of the number of prevalent individuals at each time point in the stratum; $\matr{S}$ is a matrix formed from the survival function, as defined below; and $\vec{Z}$ is a vector of the incidence at each time point in the stratum.
Dividing each side by the total number of individuals in each stratum transforms number of prevalent individuals to prevalence and incidence to incidence proportion.

Violation of assumptions in various parts of this procedure can lead to the second term in \cref{transmission:eq:forward-substitute} to be greater than the first, giving negative incidence.
In this case, the incidence prior to day $t$ imply that the prevalence on day $t$ is higher than that predicted by the fitted regression model for this strata/day combination.
There are two sets of assumptions which are most likely to be violated.
The first set of assumptions is in constructing survival matrix, $\matr{S}$, which is assumed to be known with no uncertainty in this procedure.
However, \cref{E-imperf-test} showed that the estimate of $S(t)$ is sensitive to assumptions made, such as the assumed $\psens$ and strength of priors used.
The second set of assumptions are in specifying the statistical model used to estimate prevalence, for example the form of the smoothing used.
In this context, that means the prior $\pi_P$ places non-zero mass on prevalence values which imply negative incidence under the other model assumptions.

@@

Alternative inference techniques could allow more powerful modelling approaches, if they allowed a broader set of models than LGMs.
In particular, the incidence-inferred approach could be adopted.
This could allow more interpretable priors to be used because the infection process is the process that corresponds to biological and behavioural processes.
Furthermore, the incidence proportion could be restricted to be non-negative, preventing the negative incidence seen in some strata.

Various alternative inference techniques could be considered.
If the infection process is considered a Poisson process (defined in \cref{E-inc-prev:sec:poisson-process}), then, conditional on the process's intensity, there is independence between individuals' infection status.
The conditional independence implies the incidence proportion and prevalence are the mean of many independent Bernoulli variables.
Therefore, the Central Limit Theorem implies they are approximately normally distributed.
Exploiting this property could enable efficient approximations to the posterior.
For example, a Laplace approximation or variational inference.
Further work, to check the quality of these approximations, is required.

@@

The majority of the confidence intervals contain the nominal probability (see \cref{SEIR:fig:sim-coverage}).
There is a tendency for the coverage to be slightly lower than the nominal probability, suggesting that the credible intervals are slightly too narrow.
This is a common issue with random walk MCMC (see \cref{E-MCMC:sec:improving}).
The same issue arises with the coverage for derived quantities incidence and prevalence (see \cref{SEIR:fig:sim-inc-prev}).
\begin{figure}
    \includegraphics{SEIR/sim/coverage}
    \caption[Coverage of simulation study]{%
        Point estimate and 95\% confidence interval for coverage of the 50\%, 75\%, and 95\% central credible intervals for each parameter; see text for full definition.
        Vertical lines show the nominal coverage.
    }
    \label{SEIR:fig:sim-coverage}
\end{figure}
\begin{figure}
    \thisfloatpagestyle{empty}
    \vspace{-3cm}
    \makebox[\textwidth][c]{\includegraphics[width=0.9\paperwidth]{SEIR/sim/predictive_coverage}}
    \caption[Coverage of simulation study (derived quantities)]{%
        Point estimate and 95\% confidence interval for coverage of the 50\%, 75\%, and 95\% central credible intervals for (A) incidence and (B) prevalence; see main text for full definition.
        Horizontal lines show the nominal coverage.
    }
    \label{SEIR:fig:sim-inc-prev}
\end{figure}

@@

All regions' MCMC chains converged, assessed using the Rhat statistic and ESS (as defined in \cref{E-MCMC:sec:convergence}).
The highest Rhat was 1.01 for $\sigma_\epsilon$ in London.
All parameters had ESS > 1000, except $\sigma_\epsilon$ and $\psi$ in London, which had ESS of 450 and 950 respectively.
